ODGI: understanding pangenome graphs

### 2021-11-04 manuscript/fig_extract_viz_draw_position_untangle.tex
squeeze!

            \includegraphics[width=\linewidth, trim=0cm 0cm -10cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_gfa_og_mhc_og_O_og_lay_H1000w100_png_svg}

@@

                \includegraphics[width=\linewidth, trim=0 1.7cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted}

@@

                \includegraphics[width=\linewidth, trim=0 +1.7cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted_du}

@@

                \includegraphics[width=\linewidth, trim=0 +1.7cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted_z}

@@

                \includegraphics[width=\linewidth, trim=0 +1.7cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted_m}

@@

        The top two reference genomes and 2 haplotypes (HG01952\#2) go from left to right, while 5 haplotypes go in the opposite direction, as indicated by the black color on their left.

>>>>

            \includegraphics[width=\linewidth, trim=0cm 20cm -20cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_gfa_og_mhc_og_O_og_lay_H1000w100_png_svg}

@@

                \includegraphics[width=\linewidth, trim=0 1.9cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted}

@@

                \includegraphics[width=\linewidth, trim=0 +1.9cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted_du}

@@

                \includegraphics[width=\linewidth, trim=0 +1.9cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted_z}

@@

                \includegraphics[width=\linewidth, trim=0 +1.9cm 0cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_C4_sorted_m}

@@

        The top two reference genomes and 2 haplotypes (HG01952\#2) xgo from left to right, while 5 haplotypes go in the opposite direction, as indicated by the black color on their left.
